---
title: "Study 1"
output:
  html_document: 
    toc: true
---
TODO notes:

 - get empirica time recording to behave (grumble)
 - read feedback
 
# Study 1 notes

2x2 study of BoS vs PD crossed with chat or no-chat. All did 40 trials. All did a 3 minute "turing-test" free chat at the start. Run Jan 7. Target was 20 pairs in each condition. 

## Pre-reg
According to https://osf.io/8fnze, the analyses I'm going to do:

This is exploratory research, here are some things we plan to explore. 
role of language on score. For each type of game, do games with language have higher overall scores ? Is this related to if language was actually used? 
Quantity and type of language over rounds. How much language is produced each round in PD v BoS? Does it decline in later rounds? 
What type of language is used? Is it just identifying what to select or is there meta-strategy/negotiation?
Are pairs converging to predictable strategies?

# Pre-process

```{r set-up, include=F}
knitr::opts_chunk$set(echo = FALSE, warning=F, message=F)
knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo-png"))
options(knitr.table.format = "html")
library(tidyverse)
library(jsonlite)
library(here)
library(rlang)
library(lme4)
library(brms)
library(rstan)
library(viridis)
library(knitr)

rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())
theme_set(theme_bw())

ParseJSONColumn <- function(x) {
  str_c("[ ", str_c(x, collapse = ",", sep=" "), " ]")  %>% 
    fromJSON(flatten = T)
}

##Data import constants
data_location="data/study1_220107"

date_start=lubridate::ymd('2022-01-07')

#image_location="write-ups/images"

#model_location="code/models"
```

```{r bonus}
##This was for determining participant bonuses using the version of data with PID

# d.players <- read_csv(here(data_location, 'players.csv')) %>%
#   rename(playerId=`_id`) %>%
#   select(data.bonus, playerId,id) %>%
#   mutate(bonus=round(data.bonus,2),
#          bonus=bonus %|% 0,
#          cost=round(bonus*4/3,2)) %>%
#   write_csv(here(data_location, "player_payments.csv")) %>% select(id,bonus) %>%
#   filter(bonus>0) %>% write_csv(here(data_location,"for_prolific.csv"))

```


```{r}

d.treatments <- read_csv(here(data_location, 'treatments.csv')) %>% 
  rename(treatmentId=`_id`) %>% 
  select(treatmentId, name) %>% 
  separate(name, c("game_cond", "chat_cond"))

d.games <- read_csv(here(data_location, 'games.csv')) %>% 
  rename(gameId = `_id`) %>% 
  left_join(d.treatments) %>% 
    filter(createdAt >= date_start) %>% 
  select(gameId,playerIds,game_cond,chat_cond)

d.gameplayers <- d.games %>% separate(playerIds, c("p1","p2")) %>% 
  pivot_longer(p1:p2, values_to="playerId") %>% 
  select(-name)

d.players <- read_csv(here(data_location, 'players.csv')) %>% 
  select(playerId=`_id`,role=data.role, data.bonus) %>% 
  left_join(d.gameplayers)

```

```{r, include=F, eval=F}

d.chat.raw <- read_csv(here(data_location, 'rounds.csv'), guess_max=10000) %>%
  filter(createdAt >= date_start) %>%
  mutate(data.chat = ifelse(is.na(data.chat), '{}', data.chat)) %>%
  rename(row_id = `_id`) %>%
  mutate(data.chat = map(data.chat, .f = ParseJSONColumn)) %>%
  unnest(data.chat) %>% 
  select( -ends_with('response'), -ends_with('time'), -ends_with('payoff'), -ends_with('role')) %>%
  rename_with(~ gsub("data.", "", .x, fixed = TRUE)) %>% 
  left_join(d.games) %>% 
  write_csv(here(data_location, 'raw_chat.csv'))

d.round_results.raw <- read_csv(here(data_location,'rounds.csv'),guess_max=10000) %>% 
  filter(createdAt >= date_start) %>% 
  rename_with(~ gsub("data.", "", .x, fixed = TRUE)) %>% 
  rename_with ( ~ gsub("room", "player", .x, fixed=T)) %>% 
    rename_with ( ~ gsub("player", "player_", .x, fixed=T)) %>% 
    rename_with ( ~ gsub("response", "_response", .x, fixed=T)) %>% 
  rename_with( ~ gsub("time", "_time", .x, fixed=T)) %>% 
  select(-chat) %>% 
  gather(key, value, starts_with('player')) %>% 
  separate(key, into = c('blah', 'playerId', 'info')) %>% 
  spread(info, value) %>% 
  select(-blah) %>% 
  select(-stageIds,-index,-createdAt,-submitted) %>% 
  filter(!is.na(response)) %>% 
  mutate(time=as.numeric(time)/1000) %>% 
  mutate(targets=map(targets, .f=ParseJSONColumn)) %>% 
  unnest(targets) %>% 
  mutate(image = gsub('/experiment/', '', image, fixed=TRUE),
        image = gsub('.jpeg', '', image, fixed=TRUE)) %>% 
  pivot_wider(names_from=label, names_prefix="box_", values_from=image) %>% 
    mutate(payoffs=map(payoffs, .f=ParseJSONColumn)) %>%
  unnest(payoffs) %>% 
  mutate(AA=ifelse(role=="p1", AA.p1, AA.p2),
         AB=ifelse(role=="p1", AB.p1, AB.p2),
         BA=ifelse(role=="p1", BA.p1, BA.p2),
         BB=ifelse(role=="p1", BB.p1, BB.p2)) %>% 
  left_join(d.games) 

d.exit.survey <- read_csv(here(data_location, 'player-inputs.csv')) %>%
  filter(createdAt >= date_start) %>%
  left_join(d.games, by = c('gameId')) %>%
    rename_with(~ gsub("data.", "", .x, fixed = TRUE)) 

d.complete <- d.round_results.raw %>% group_by(gameId, playerId) %>% 
  summarize(max_rep=max(repNum)) %>% filter(max_rep==39) %>% select(gameId,playerId) %>% 
  write_csv(here(data_location,"complete.csv"))

#remove that one game that didn't complete
d.chat <- d.chat.raw %>% inner_join(d.complete) %>% 
  write_csv(here(data_location, 'raw_chat.csv'))
d.round_results <- d.round_results.raw %>% inner_join(d.complete) %>% 
  write_csv(here(data_location, 'raw_results.csv'))
d.exit <- d.exit.survey %>% inner_join(d.complete) %>% 
  write_csv(here(data_location,'exit.csv'))

```

# Game length
Estimated 15 mins total including intro/exit/waiting turing etc

How long did people spend playing? (Not counting intro chat round)

```{r total-time}
# game KxJzRQeo5HikZxreo, player BkAWA2P83AnBmRcif has consistently unreasonable times (3300+, should be <180, so something's messing up)

d.round_results <- read_csv(here(data_location,"raw_results.csv"))

summary <- d.round_results %>% group_by(repNum, gameId, game_cond, chat_cond) %>% 
  filter(time<181) %>% 
  summarize(max_time=max(time)) %>% 
  group_by(gameId, game_cond, chat_cond) %>% 
  summarize(total_time=sum(max_time)/60,
            num_rounds=max(repNum))

ggplot(summary, aes(x=str_c(game_cond," ", chat_cond), y=total_time, color=str_c(game_cond," ", chat_cond)))+geom_jitter(width=.1)+  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width=.3), size=.5,color="black")+
  labs(title="Game time in min", y="mins", x="condition")+theme(legend.position = "none")

summary %>% group_by(game_cond, chat_cond) %>% tally()
```
A respectable rate of game completion. 

# Bonuses

Note that bonuses are not directly comparable between BoS & PD! 
But it looks like chat helps in BoS and not (much?) in PD. 

```{r}
pairs <- d.round_results %>% select(playerId,gameId) %>% unique()
bonuses <- d.players %>%inner_join(pairs) %>%  select(playerId,data.bonus, chat_cond, game_cond) %>% filter(!is.na(data.bonus)) %>% left_join(pairs) %>% arrange(gameId)

ggplot(bonuses, aes(x=str_c(game_cond," ", chat_cond), y=data.bonus, color=str_c(game_cond," ", chat_cond)))+geom_jitter(width=.1)+
  labs(title="Bonus earned", y="bonus", x="condition")+  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width=.3), size=.5,color="black")+theme(legend.position = "none")+scale_y_continuous(limits=c(0,6))
```

# Pre-chat 
```{r}
#this is a sloppy way to split, but eh, 
chat <- read_csv(here(data_location, "raw_chat.csv")) %>% filter(!is.na(text)) %>% filter(is.na(targets)) %>% 
  mutate(words=str_count(text, "\\w+")) %>%  group_by(gameId, playerId, chat_cond, game_cond) %>% summarize(words=sum(words))

ggplot(chat, aes(x=str_c(game_cond," ", chat_cond), y=words))+geom_jitter(width=.1)+
  labs(title="Words produced in pre-chat", y="words", x="condition")
```

People talked some. I haven't looked at the transcripts at all. 

# During chat

This chat is raw. There are outliers that have been chopped off. 
People talk more during BoS than PD. 

```{r}
game_chat <- read_csv(here(data_location, "raw_chat.csv")) %>% filter(!is.na(targets)) %>% filter(chat_cond=="chat") %>% 
  mutate(words=str_count(text, "\\w+") %|% int(0)) %>%  group_by(gameId, playerId, game_cond, repNum) %>% summarize(words=sum(words))

chat_by_game <- game_chat %>% group_by(gameId, game_cond, repNum) %>% summarize(words=sum(words))

is_chat <- chat_by_game %>% mutate(is.chat=ifelse(words>0, 1,0)) %>% group_by(game_cond, repNum) %>% summarize(pct_chat=mean(is.chat))

ggplot(game_chat, aes(x=repNum, y=words, color=game_cond))+geom_jitter(width=.1, size=1, alpha=.2)+facet_wrap(~game_cond)+scale_y_continuous(limits=c(0,30))+
  geom_smooth()+
  labs(title="Words produced per round per player", y="words")

ggplot(chat_by_game, aes(x=repNum, y=words, color=game_cond))+geom_jitter(width=.1, size=1, alpha=.2)+facet_wrap(~game_cond)+scale_y_continuous(limits=c(0,30))+
  geom_smooth()+
  labs(title="Words produced per round per game", y="words")

ggplot(is_chat, aes(x=repNum, y=pct_chat, color=game_cond))+geom_point()+
  labs(title="Pct games who said anything", y="pct")
```

Currently open questions -- is that game-related chat, or is it just that it's a friendlier game? 
Does the chatting help? 

## What are people saying? 

```{r}
library(qdap)

game_chat %>% ungroup() %>%  summarize(s=sum(words)) #2093 total words

chat <-  read_csv(here(data_location, "raw_chat.csv")) %>%
  filter(!is.na(targets)) %>% 
  filter(chat_cond=="chat") %>% 
  filter(!is.na(text)) %>% 
  select(gameId,game_cond,repNum, text) %>% 
  mutate(text=strip(text)) %>% 
  mutate(length=str_count(text, "\\w+")) %>% 
  filter(length>0)

ggplot(chat, aes(length))+geom_bar()

```

Most utterances are single word utterances, we'll consider these and multi word utterances separately. 

```{r}
#single world
words <- chat %>% filter(length==1) %>% pull(text) %>% word_list() %>% pull(fwl) 

head(words$all, 20)
#chat %>% filter(length==1) %>% nrow()
colors <- c("green", "blue", "pink","purple", "yellow", "red", "orange", "brown", "grey","white", "salmon", "gray")

chat %>% filter(length==1) %>% filter(text %in% colors) %>% nrow()
```

There are 743 singletons. Of these 100 are ok/okay, at least 433 are color words, more once you count rarities and misspellings. There's also a bunch of singleton letters -- these seem to be single letter color abbreviations?

From skimming transcripts, looks like multi's occur earlier in general. But we're confounded by pleasantries at random times (talking about where they live, etc). 

```{r}

chat %>% mutate(singleton=ifelse(length==1, "single", "multi")) %>% ggplot(aes(repNum, fill=singleton))+geom_bar()+facet_grid(singleton~game_cond)

```

```{r}
chat %>% filter(length>1) %>% select(game_cond, repNum, text) %>% head(40) %>% knitr::kable()

```
# Does chat help? 

To look at if chatting helps -- we can compare forced no-chat to chat (see bonuses above). We can also compare used chat (0/1 or amount) within those that could chat. 

Options for dependent variable are bonus (although there's some noise there) or option chosen. 

```{r}

group_chat <- chat_by_game %>% mutate(is.chat=ifelse(words>0, 1,0)) %>% group_by(game_cond, gameId) %>% summarize(pct_chat=mean(is.chat))

all <- d.players %>% left_join(group_chat) %>% filter(data.bonus>0)

ggplot(all, aes(x=pct_chat, y=data.bonus, color=game_cond))+geom_point()

```

Looks like chatting helps for BoS, doesn't get used much for PD. 

## Choices 

In BoS: P1 prefers AA to BB, P2 prefers BB to AA. AB and BA are bad for both. 

In PD: P1 prefers BA > AA > BB > AB and P2 prefers AB > AA > BB > BA. (BB is Nash equilibrium, AA is Pareto dominant.)

Not really sure how to visualize this efficiently? 

Being in the chat condition v not
 
```{r}
outcome <- d.round_results %>% select(gameId:repNum, response,role, game_cond, chat_cond) %>% 
  pivot_wider(names_from=role, values_from=response) %>% 
  mutate(outcome=str_c(p1,p2))

ggplot(outcome, aes(x=repNum, y=outcome))+geom_jitter(width=.1, alpha=.25)+facet_grid(game_cond~chat_cond)+theme(legend.position="none")

outcome_summary <- outcome %>% group_by(game_cond, chat_cond, repNum,outcome) %>% tally() %>% group_by(game_cond, chat_cond, repNum) %>% summarize(pct=n/sum(n), outcome=outcome)

ggplot(outcome_summary, aes(x=repNum, y=pct, color=chat_cond))+geom_line()+facet_grid(game_cond~outcome)

```

Actually using the chat that round

```{r}
outcome <- d.round_results %>% select(gameId:repNum, response,role, game_cond, chat_cond) %>% 
  pivot_wider(names_from=role, values_from=response) %>% 
  mutate(outcome=str_c(p1,p2)) %>% filter(chat_cond=="chat") %>% left_join(chat_by_game) %>% mutate(is.chat=ifelse(words>0, 1,0))

outcome_summary <- outcome %>% group_by(game_cond, is.chat, repNum,outcome) %>% tally() %>% group_by(game_cond, is.chat, repNum) %>% summarize(pct=n/sum(n), outcome=outcome)

ggplot(outcome_summary, aes(x=repNum, y=pct, color=as.factor(is.chat)))+geom_line()+facet_grid(game_cond~outcome)

```


# Is the other player a human? 

```{r bot}

bot <- read_csv(here(data_location, "exit.csv")) %>% 
  filter(!is.na(game_cond) & !is.na(chat_cond)) %>% 
  group_by(game_cond, chat_cond, human) %>% 
  tally() %>% 
  pivot_wider(names_from=human, values_from=n)

bot
```

Only 10-20% of players think the other person is a bot! 

