---
title: "Expt 5: Mix of PD and BoS with spikes and two types of PD trials"
output:
  html_document: 
    toc: true
---

  

```{r set-up, include=F}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F)
knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo-png"), fig.width=7, fig.height=3)
options(knitr.table.format = "html")
library(tidyverse)
library(jsonlite)
library(here)
library(rlang)
library(viridis)
library(knitr)
theme_set(theme_bw())

ParseJSONColumn <- function(x) {
  str_c("[ ", str_c(x, collapse = ",", sep = " "), " ]") %>%
    fromJSON(flatten = T)
}

## Data import constants
data_location <- "data/study5_241028"

date_start <- lubridate::ymd("2024-10-26")

image_location <- "write-ups/images"

model_location <- "code/models"
```


Note: one participant wasn't getting a partner, so they opened up a new tab, fiddled with the id and played themselves. 
So we exclude the game with player id YSB8RYRgF2tQjym2e, which is game AQXAv4FKrZxBrTQgE 

```{r bonus}


## This is for determining participant bonuses using the version of data with PID

# d.players <- read_csv(here(data_location, 'players.csv')) %>%
#   rename(playerId=`_id`) %>%
#   select(data.bonus, playerId,id) %>%
#   mutate(bonus=round(data.bonus,2),
#          bonus=bonus %|% 0,
#          cost=round(bonus*4/3,2)) 
#   write_csv(here(data_location, "player_payments.csv")) %>% select(id,bonus) %>%
#   filter(bonus>0) %>% write_csv(here(data_location,"for_prolific.csv"))
# #
# cost <- read_csv(here(data_location,"player_payments.csv"))
# #
# sum(cost$cost)
```

# Summary 

Each game has:

 - 4 "spiked" BoS trials where one of the rewards is high (25-30) and the other is normal (3-7)
 
 - ~16 normal BoS trials where both rewards are from [1-9]
 
 - ~10 normal ("easy") PD trials where cooperating is welfare maximizing ( 2 * coop payoff greater than or equal to defect payoff). All rewards are chosen from [1-12] respecting this.
 
 - ~10 “sacrifice” ("hard") PD trials where having one person defect and the other take the sucker payoff is welfare maximizing (the defect payoff is > 2 * coop payoff). All rewards are chosen from [1-12] respecting this. 



```{r, include=F, eval=F}
d.treatments <- read_csv(here(data_location, "treatments.csv")) %>%
  rename(treatmentId = `_id`) %>%
  select(treatmentId, name) |>
  mutate(
    chat_cond = ifelse(str_detect(name, "no chat"), "no_chat", "chat"),
    game_cond = "oct2024"
  )

d.games <- read_csv(here(data_location, "games.csv")) %>%
  rename(gameId = `_id`) %>%
  left_join(d.treatments) %>%
  filter(createdAt >= date_start) %>%
  select(gameId, playerIds, game_cond, chat_cond)

d.gameplayers <- d.games %>%
  separate(playerIds, c("p1", "p2")) %>%
  pivot_longer(p1:p2, values_to = "playerId") %>%
  select(-name)

d.players <- read_csv(here(data_location, "players.csv")) %>%
  select(playerId = `_id`, role = data.role, data.bonus) %>%
  left_join(d.gameplayers)
```

```{r, include=F, eval=F}
d.chat.raw <- read_csv(here(data_location, "rounds.csv"), guess_max = 10000) %>%
  filter(createdAt >= date_start) %>%
  mutate(data.chat = ifelse(is.na(data.chat), "{}", data.chat)) %>%
  rename(row_id = `_id`) %>%
  mutate(data.chat = map(data.chat, .f = ParseJSONColumn)) %>%
  unnest(data.chat) %>%
  select(-ends_with("response"), -ends_with("time"), -ends_with("payoff"), -ends_with("role")) %>%
  rename(data.gametype = data.type) %>% # VB 220413:this fixes a collision with the "type" column
  rename_with(~ gsub("data.", "", .x, fixed = TRUE)) %>%
  left_join(d.games) %>%
  write_csv(here(data_location, "raw_chat.csv"))

d.round_results.raw <- read_csv(here(data_location, "rounds.csv"), guess_max = 10000) %>%
  filter(createdAt >= date_start) %>%
  rename(data.gametype = data.type) %>% # VB 220413:this fixes a collision with the "type" column
  rename_with(~ gsub("data.", "", .x, fixed = TRUE)) %>%
  rename_with(~ gsub("room", "player", .x, fixed = T)) %>%
  rename_with(~ gsub("player", "player_", .x, fixed = T)) %>%
  rename_with(~ gsub("response", "_response", .x, fixed = T)) %>%
  rename_with(~ gsub("time", "_time", .x, fixed = T)) %>%
  select(-chat) %>%
  gather(key, value, starts_with("player")) %>%
  separate(key, into = c("blah", "playerId", "info")) %>%
  spread(info, value) %>%
  select(-blah) %>%
  select(-stageIds, -index, -createdAt, -submitted) %>%
  filter(!is.na(response)) %>%
  mutate(time = as.numeric(time) / 1000) %>%
  mutate(targets = map(targets, .f = ParseJSONColumn)) %>%
  unnest(targets) %>%
  mutate(
    image = gsub("/experiment/", "", image, fixed = TRUE),
    image = gsub(".jpeg", "", image, fixed = TRUE)
  ) %>%
  pivot_wider(names_from = label, names_prefix = "box_", values_from = image) %>%
  mutate(payoffs = map(payoffs, .f = ParseJSONColumn)) %>%
  unnest(payoffs) %>%
  mutate(
    AA = ifelse(role == "p1", AA.p1, AA.p2),
    AB = ifelse(role == "p1", AB.p1, AB.p2),
    BA = ifelse(role == "p1", BA.p1, BA.p2),
    BB = ifelse(role == "p1", BB.p1, BB.p2),
    type = ifelse(AB == 0 & BA == 0, "BoS", "PD")
  ) %>%
  left_join(d.games)

d.exit.survey <- read_csv(here(data_location, "player-inputs.csv")) %>%
  filter(createdAt >= date_start) %>%
  left_join(d.games, by = c("gameId")) %>%
  rename_with(~ gsub("data.", "", .x, fixed = TRUE))

d.complete <- d.round_results.raw %>%
  group_by(gameId, playerId) %>%
  summarize(max_rep = max(repNum)) %>%
  filter(max_rep == 39) %>%
  select(gameId, playerId) %>%
  filter(gameId!="AQXAv4FKrZxBrTQgE") |> # the game where someone was clever and played themselves
  write_csv(here(data_location, "complete.csv"))

d.chat <- d.chat.raw %>%
  inner_join(d.complete) %>%
  write_csv(here(data_location, "raw_chat.csv"))
d.round_results <- d.round_results.raw %>%
  inner_join(d.complete) %>%
  write_csv(here(data_location, "raw_results.csv"))
d.exit <- d.exit.survey %>%
  inner_join(d.complete) %>%
  write_csv(here(data_location, "exit.csv"))
```

53 games in each condition 

```{r}
read_csv(here(data_location,"raw_results.csv")) |> select(chat_cond, gameId) |> unique() |> group_by(chat_cond) |> tally()

```

# Are they human?

```{r bot}
exit <- read_csv(here(data_location, "exit.csv"))

exit %>%
  group_by(game_cond, chat_cond, human) %>%
  tally() %>%
  pivot_wider(names_from = human, values_from = n) %>%
  mutate(pct = yes / (no + yes))
```
mostly think partner is human, oh good. 

```{r}
chat <- read_csv(here(data_location, "raw_chat.csv")) %>%
  select(gameId, text, type, repNum, playerId, chat_cond, gametype, targets)

rounds <- read_csv(here(data_location, "raw_results.csv")) %>%
  select(gameId, repNum, playerId, payoff, response, time, box_A, box_B, AA, AB, BA, BB, chat_cond, gametype, role)
```

# Before chat 

```{r}
games <- rounds |>
  select(gameId, chat_cond) |>
  unique()

before_chat <- chat |>
  filter(is.na(targets)) |>
  mutate(words = str_count(text, "\\W+") %|% int(0)) |>
  group_by(gameId, chat_cond) |>
  summarize(words = sum(words)) |>
  full_join(games)

ggplot(before_chat, aes(x = chat_cond, y = words)) +
  geom_jitter(width = .1, color = "blue", alpha = .5) +
  stat_summary(fun.data = "mean_cl_boot")
```

People do talk to each other a little in the pre-game chat time. 

# Points earned

Note that BoS has a lower points range than PD because of what range of random numbers is selected. 

```{r}
bonuses <- rounds %>%
  group_by(playerId, gameId, chat_cond, gametype) %>%
  summarize(payoff = mean(payoff))



ggplot(bonuses, aes(x = chat_cond, y = payoff, color = str_c(chat_cond))) +
  geom_jitter(width = .1, alpha = .1) +
  facet_grid(. ~ gametype) +
  scale_color_viridis(discrete = T) +
  labs(y = "mean_reward", x = "condition") +
  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width = .3), size = .7, color = "black", geom="errorbar") +
    stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width = .3), size = .7, color = "black") +
  theme(legend.position = "none") +
  coord_cartesian(ylim = c(0, 20)) +
  labs(y = "Mean reward / trial") +
  theme(
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 14),
    strip.text = element_text(size = 14)
  )
```

Looks like chat does better in spike, and a little bit on normal BoS?

# During chat

```{r}
game_chat <- chat %>%
  filter(!is.na(targets)) %>%
  select(-type) %>%
  full_join(rounds) %>%
  mutate(words = str_count(text, "\\W+") %|% int(0)) |>
  group_by(gameId, gametype, chat_cond, repNum) %>%
  summarize(
    words = sum(words),
    mean_payout = mean(payoff),
    is_chat = ifelse(words > 0, 1, 0)
  )



when_chat <- game_chat %>%
  filter(chat_cond == "chat") |>
  mutate(is.chat = ifelse(words > 0, 1, 0)) %>%
  group_by(repNum, gametype) %>%
  summarize(pct_chat = mean(is.chat))

ggplot(when_chat, aes(x = repNum, y = pct_chat, color = gametype)) +
  geom_point() +
  geom_smooth(method = "lm") +
  coord_cartesian(ylim=c(0,1))+
  labs(title = "pct of games who said anything each round")

how_many_chat <- game_chat |> filter(chat_cond == "chat") |>
  mutate(is.chat = ifelse(words > 0, 1, 0)) %>%
  group_by(gameId) %>%
  summarize(pct_chat = mean(is.chat)) |> 
  arrange(pct_chat)


#how_many_chat |> nrow()
#how_many_chat |> filter(pct_chat>=.1) |> nrow()

how_many_chat |> 
  mutate(x=1/n()*row_number()) |> ggplot(aes(x=x, y=pct_chat))+geom_point()+
    coord_cartesian(ylim=c(0,1))+geom_hline(yintercept=.1)+geom_hline(yintercept=.5)+labs(title="Game 5")

```
Not a lot of talking. 

## Per trial does more talking help

 - chat_0 is had access to chat and didn't use on that trial
 - chat_1 is used chat on that trial
 - nochat_0 did not have access to chat 
 
```{r}
ggplot(game_chat, aes(x = str_c(chat_cond, "_", is_chat), y = mean_payout)) +
  stat_summary(fun.data = "mean_cl_boot", geom="errorbar") +
    stat_summary(fun.data = "mean_cl_boot") +

  facet_grid(. ~ gametype) +
  geom_smooth(method = "lm")
```

Looks like mostly the actually using the chat is what's helping. 

Looks like using language is correlated with better outcome with BoS and slightly better outcome for PD. But if this language helping or "people who avail themselves of the option to use language are more competent". 

Is there a dose-response relationship, or is one word enough?

```{r}
ggplot(game_chat |> filter(words > 0), aes(x = log(words), y = mean_payout)) +
  geom_point() +
  facet_grid(. ~ gametype) +
  geom_smooth(method = "lm")
```

Especially where we have more data, looks like one word is enough. Indicative of coordination rather than negotiation, probably? 

## Per game does talking help?

One idea is that talking on some trials may set up coordination strategies that can then effectively be used on later trials without talking on those trials. 

So we want to look at overall volume of talking (in words or in # of trial talked) as a predictor for performance, controlling for talk on that round? 

```{r}
group_talk <- game_chat |>
  group_by(gameId) |>
  summarize(total_words = sum(words), pct_chat = mean(is_chat))

overall_talk <- game_chat |> left_join(group_talk)

ggplot(overall_talk |> filter(chat_cond == "chat"), aes(x = pct_chat, y = mean_payout, color = as.character(is_chat))) +
  geom_jitter(alpha = .1) +
  geom_smooth(method = "lm") +
  facet_grid(. ~ gametype) +
  theme(legend.position = "bottom")
```

Looks like talking on *other* trials might help in BoS if you didn't talk on this specific trial? But might just be fitting to outliers? Will need models. 

# Option selected

 - chat_0 is had access to chat and didn't use on that trial
 - chat_1 is used chat on that trial
 - nochat_0 did not have access to chat 
 


```{r}
outcome <- rounds %>%
  select(gameId, repNum, response, chat_cond, gametype, role) |>
  pivot_wider(names_from = role, values_from = response) %>%
  mutate(outcome = str_c(p1, p2)) %>%
  left_join(game_chat)
```

## BoS

In BoS: P1 prefers AA to BB, P2 prefers BB to AA. AB and BA are 0 for both. 

```{r}
outcome %>%
  filter(gametype == "BoS") %>%
  mutate(outcome_parity = ifelse(outcome %in% c("AA", "BB"), 1, 0)) %>%
  ggplot(aes(x = str_c(chat_cond, "_", is_chat), y = outcome_parity)) +
  stat_summary(fun.data = "mean_cl_boot") +
  geom_hline(aes(yintercept = .5)) +
  labs(title = "BoS:fraction choosing good outcomes (AA or BB)", y = "Good outcome?")
```

Near chance if you can't talk, or if you don't talk, far above chance if you do coordinate. 

```{r}
outcome %>%
  filter(gametype == "BoS") %>%
  mutate(outcome_parity = ifelse(outcome %in% c("AA", "BB"), 1, 0)) %>%
  ggplot(aes(x = repNum, y = outcome_parity)) +
  facet_grid(~ str_c(chat_cond, "_", is_chat)) +
  stat_summary(fun.data="mean_cl_boot", geom="point")+
  geom_smooth(method = "lm", se = F) +
  geom_hline(aes(yintercept = .5)) +
  labs(title = "BoS:fraction choosing good outcomes", y = "Good outcome?")
```

## spike BoS

```{r}
outcome %>%
  filter(gametype == "spikeBoS") %>%
  mutate(outcome_parity = ifelse(outcome %in% c("AA", "BB"), 1, 0)) %>%
  ggplot(aes(x = str_c(chat_cond, "_", is_chat), y = outcome_parity)) +
  stat_summary(fun.data = "mean_cl_boot") +
  geom_hline(aes(yintercept = .5)) +
  labs(title = "Spiked BoS:fraction choosing good outcomes (AA or BB)", y = "Good outcome?")

outcome %>%
  filter(gametype == "spikeBoS") %>%
  mutate(outcome_parity = ifelse(outcome %in% c("AA", "BB"), 1, 0)) %>%
  ggplot(aes(x = repNum, y = outcome_parity)) +
  facet_grid(~ str_c(chat_cond, "_", is_chat)) +
  stat_summary(fun.data="mean_cl_boot", geom="point")+
  geom_smooth(method = "lm", se = F) +
  geom_hline(aes(yintercept = .5)) +
  labs(title = "spike BoS:fraction choosing good outcomes", y = "Good outcome?")
```

## easy PD

In easyPD: P1 prefers BA > AA > BB > AB and P2 prefers AB > AA > BB > BA. AA is welfare maximizing.


```{r}
outcome %>%
  filter(gametype == "easyPD") %>%
  mutate(AA = ifelse(outcome %in% c("AA"), 1, 0), 
         AB.BA =ifelse(outcome %in% c("AB", "BA"), 1, 0), 
         BB = ifelse(outcome %in% c("BB"), 1, 0)) %>%
  pivot_longer(AA:BB, names_to="type", values_to="selected") |> 
  ggplot(aes(x = str_c(chat_cond, "_", is_chat), y = selected, color=type)) +
  stat_summary(fun.data = "mean_cl_boot") +
  geom_hline(aes(yintercept = .5)) 
```

Can get a reasonable option no matter what. 

```{r}
outcome %>%
  filter(gametype == "easyPD") %>%
  mutate(AA = ifelse(outcome %in% c("AA"), 1, 0), 
         AB.BA =ifelse(outcome %in% c("AB", "BA"), 1, 0), 
         BB = ifelse(outcome %in% c("BB"), 1, 0)) %>%
  pivot_longer(AA:BB, names_to="type", values_to="selected") |> 
  ggplot(aes(x = repNum, y = selected, color=type)) +
  stat_summary(fun.data = "mean_cl_boot", geom="point", alpha=.5) +
  facet_grid(.~str_c(chat_cond, "_", is_chat))+
  geom_smooth(method="lm")+
  geom_hline(aes(yintercept = .5)) 
```


## hard PD

In hard PD: P1 prefers BA > AA > BB > AB and P2 prefers AB > AA > BB > BA. AB/BA is welfare maximizing.


```{r}
outcome %>%
  filter(gametype == "hardPD") %>%
  mutate(AA = ifelse(outcome %in% c("AA"), 1, 0), 
         AB.BA =ifelse(outcome %in% c("AB", "BA"), 1, 0), 
         BB = ifelse(outcome %in% c("BB"), 1, 0)) %>%
  pivot_longer(AA:BB, names_to="type", values_to="selected") |> 
  ggplot(aes(x = str_c(chat_cond, "_", is_chat), y = selected, color=type)) +
  stat_summary(fun.data = "mean_cl_boot") +
  geom_hline(aes(yintercept = .5)) 
```
So if you do use the chat, you tend to get the best option. (Using chat means that easy and hard PD look different)

Whereas if you don't chat, they look more similar at least. 

```{r}
outcome %>%
  filter(gametype == "hardPD") %>%
  mutate(AA = ifelse(outcome %in% c("AA"), 1, 0), 
         AB.BA =ifelse(outcome %in% c("AB", "BA"), 1, 0), 
         BB = ifelse(outcome %in% c("BB"), 1, 0)) %>%
  pivot_longer(AA:BB, names_to="type", values_to="selected") |> 
  ggplot(aes(x = repNum, y = selected, color=type)) +
  stat_summary(fun.data = "mean_cl_boot", geom="point", alpha=.5) +
  facet_grid(.~str_c(chat_cond, "_", is_chat))+
  geom_smooth(method="lm")+
  geom_hline(aes(yintercept = .5)) 
```


# Language 

How much language? 

Filter only for games that talked at least a little. 

Second graph filters for *trials* that talked. 

```{r}
game_chat |>
  group_by(gameId) |>
  summarize(total_words = sum(words)) |>
  filter(total_words != 0) |>
  left_join(game_chat) |>
  ggplot(aes(x = repNum, y = words)) +
  geom_point(alpha = .1) +
  geom_smooth()

game_chat |>
  group_by(gameId) |>
  summarize(total_words = sum(words)) |>
  filter(total_words != 0) |>
  left_join(game_chat) |>
  filter(words > 0) |>
  ggplot(aes(x = repNum, y = words)) +
  geom_point(alpha = .1) +
  geom_smooth()
```

## how often do *both* people talk

```{r}
pair_chat <- chat %>%
  filter(!is.na(targets)) %>%
  select(-type) %>%
  full_join(rounds) %>%
  mutate(words = str_count(text, "\\W+") %|% int(0)) |>
  group_by(gameId, playerId, gametype, chat_cond, repNum) %>%
  summarize(
    words = sum(words),
    is_chat = ifelse(words > 0, 1, 0)
  ) |> 
  group_by(gameId, gametype, chat_cond, repNum) |>
  summarize(how_many_chat = sum(is_chat)) |> 
  group_by(gameId, gametype, chat_cond) |>
  summarize(pct_both = mean(how_many_chat == 2),
            pct_either=mean(how_many_chat > 0)) |> 
  filter(chat_cond == "chat") |> 
  pivot_longer(pct_both:pct_either)

ggplot(pair_chat, aes(x = gametype, y = value, color=name, group=name)) +
  geom_point(position=position_jitterdodge(dodge.width=.7,jitter.width = .2)) +
  stat_summary(fun.data = "mean_cl_boot", color = "black", position=position_dodge(.7))
```

Even in games that talk, there aren't *that* many trials where both people talk? 

<!--
# Models

```{r,eval=F}
game_chat <- chat %>%
  filter(!is.na(targets)) %>%
  select(-type) %>%
  full_join(rounds) %>%
  mutate(words = str_count(text, "\\W+") %|% int(0)) |>
  group_by(gameId, gametype, chat_cond, repNum) %>%
  summarize(
    words = sum(words),
    mean_payout = mean(payoff),
    is_chat = ifelse(words > 0, 1, 0)
  )

never_chat <- game_chat |>
  group_by(gameId, chat_cond) |>
  summarize(words = sum(words)) |>
  mutate(use_chat = ifelse(words > 0, 1, 0))

for_mod <- rounds |>
  select(gameId, repNum, playerId, payoff, chat_cond, gametype) |>
  left_join(game_chat) |>
  left_join(never_chat) |>
  mutate(
    has_chat = ifelse(chat_cond == "chat", 1, 0),
    is_BoS = ifelse(gametype == "BoS", 1, 0)
  ) # recode with no-chat PD as baseline
```

## Condition assignment on performance

```{r, eval=F}
perf_priors <- c(
  set_prior("normal(5,2)", class = "Intercept"),
  set_prior("normal(0, 2)", class = "b"),
  set_prior("normal(0, 2)", class = "sd"),
  set_prior("lkj(1)", class = "cor")
)

perf_mod <- brm(
  payoff ~ has_chat * is_BoS + repNum +
    (is_BoS | gameId) +
    (is_BoS | playerId),
  data = for_mod,
  prior = perf_priors,
  file = here(model_location, "perf_expt1"),
  control = list(adapt_delta = .95)
)

summary(perf_mod)
```

Note the high group level variability...

## Words over time 

log(words) ~ game_type * trial_number

```{r, eval=F}
for_log_words <- for_mod |>
  filter(words > 0) |>
  mutate(log_words = log(words))

lang_priors <- c(
  set_prior("normal(5,5)", class = "Intercept"),
  set_prior("normal(0, 5)", class = "b"),
  set_prior("normal(0, 5)", class = "sd"),
  set_prior("lkj(1)", class = "cor")
)

log_words_mod <- brm(
  log_words ~ is_BoS * repNum +
    (is_BoS * repNum | gameId),
  data = for_log_words,
  file = here(model_location, "words_expt1"),
  prior = lang_priors,
  control = list(adapt_delta = .95)
)
summary(log_words_mod)
```

More talk in BoS

## Words on outcome

outcome ~ game_type * log(words)

```{r, eval=F}
perf_word_mod <- brm(
  payoff ~ log_words * is_BoS + repNum +
    (is_BoS | gameId) +
    (is_BoS | playerId),
  data = for_log_words,
  prior = perf_priors,
  file = here(model_location, "perf_words_expt1"),
  control = list(adapt_delta = .99)
)

summary(perf_word_mod)
```

Again, big group level variation. 

# What people say strategy is

```{r, eval=F}
exit <- read_csv(here(data_location, "exit.csv")) |> select(chat_cond, strategy) |> filter(!is.na(strategy))

message("chat")
kable(exit |> filter(chat_cond=="chat") |> select(-chat_cond))


message("no-chat")
kable(exit |> filter(chat_cond=="no_chat") |> select(-chat_cond))


```

# In game talk

note that there's some non-game-relevant chit-chat that hasn't been cleaned up!

```{r, eval=F}
color_words <- c("red","blue", "purple", "green","yellow", "brown", "pink", "violet","cyan", "grey", "peach", "purplish", "beige", "orange")
agreement_words <- c("okay", "ok", "yes", "sure")
color_regex <- str_c(color_words, collapse="|")
agreement_regex <- str_c(agreement_words, collapse="|")

in_game_said <- chat %>%
  filter(!is.na(targets)) %>%
  select(-type) %>%
  full_join(rounds) |> filter(!is.na(text)) |>  mutate(gameId=str_sub(gameId, 1,3), playerId=str_sub(playerId, 1,3)) |> select(gameId, playerId, repNum, gametype, text) |> 
  mutate(has_color=str_detect(str_to_lower(text), color_regex),
         has_agree=str_detect(str_to_lower(text), agreement_regex))

in_game_said |> group_by(has_color) |> tally()
in_game_said |> group_by(has_agree) |> tally()


kable(in_game_said |> select(-has_color, -has_agree))
```

-->